19Q2

### 2019-09-27 19Q2.Rmd
Remake histology distributions

**RUN THIS WHEN CRISPR IS DONE MERGING (5/17)**
```{r histology_dists_data, eval=FALSE}
ccle_hists <- unique(select(ccle, DepMap_ID, disease)) %>% count(disease)
ccle_hists$Perc <- ccle_hists$n / sum(ccle_hists$n) * 100
ccle_hists$Dataset <- "CCLE"
ctrp_hists <- unique(select(ctrp, DepMap_ID, disease)) %>% count(disease)
ctrp_hists$Perc <- ctrp_hists$n / sum(ctrp_hists$n) * 100
ctrp_hists$Dataset <- "CTRP"
gdsc_hists <- unique(select(gdsc, DepMap_ID, disease)) %>% count(disease)
gdsc_hists$Perc <- gdsc_hists$n / sum(gdsc_hists$n) * 100
gdsc_hists$Dataset <- "GDSC"
crispr_hists <- unique(select(crispr, DepMap_ID, disease)) %>% count(disease)
crispr_hists$Perc <- crispr_hists$n / sum(crispr_hists$n) * 100
crispr_hists$Dataset <- "CRISPR"

@@

**RUN THIS WHEN CRISPR IS DONE MERGING (5/17)**
```{r, eval=FALSE}
ccle_ccls <- unique(ccle$DepMap_ID)
ctrp_ccls <- unique(ctrp$DepMap_ID)
gdsc_ccls <- unique(gdsc$DepMap_ID)
crispr_ccls <- unique(crispr$DepMap_ID)

@@

png(filename = "./plots/manuscript/drug_histology_distributions.png", width = 8, height = 4, units = "in", res = 500)
ggplot(all_ccls, aes(x = fct_infreq(factor(disease)), fill = disease)) +
  geom_bar(color = "black") +
  scale_y_continuous(breaks = seq(0, 220, by = 40), labels = seq(0, 220, by = 40)) +
  guides(fill = FALSE) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)) +
  labs(y = "Number of Cell Lines", x = "Histology", caption = paste0(formatC(nrow(all_ccls), format = "d", big.mark = ","), " cell lines represented."))
dev.off()
```

>>>>

```{r histology_dists_data, eval=FALSE}
ccle_hists <- unique(select(ccle, DepMap_ID, disease)) %>% count(disease)
ccle_hists$Perc <- ccle_hists$n / sum(ccle_hists$n) * 100
ccle_hists$Dataset <- "CCLE"
ctrp_hists <- unique(select(ctrp, DepMap_ID, disease)) %>% count(disease)
ctrp_hists$Perc <- ctrp_hists$n / sum(ctrp_hists$n) * 100
ctrp_hists$Dataset <- "CTRP"
gdsc_hists <- unique(select(gdsc, DepMap_ID, disease)) %>% count(disease)
gdsc_hists$Perc <- gdsc_hists$n / sum(gdsc_hists$n) * 100
gdsc_hists$Dataset <- "GDSC"
crispr_hists <- unique(select(crispr, DepMap_ID, disease)) %>% count(disease)
crispr_hists$Perc <- crispr_hists$n / sum(crispr_hists$n) * 100
crispr_hists$Dataset <- "CRISPR"

@@

```{r, eval=FALSE}
ccle_ccls <- unique(ccle$DepMap_ID)
ctrp_ccls <- unique(ctrp$DepMap_ID)
gdsc_ccls <- unique(gdsc$DepMap_ID)
crispr_ccls <- unique(crispr$DepMap_ID)

@@

png(filename = "./plots/manuscript/drug_histology_distributions.png", width = 8, height = 4, units = "in", res = 500)
ggplot(all_ccls, aes(x = fct_infreq(factor(disease)), fill = disease)) +
  geom_bar(color = "black") +
  scale_y_continuous(breaks = seq(0, 220, by = 40), labels = seq(0, 220, by = 40)) +
  guides(fill = FALSE) +
  theme(axis.text.x = element_text(angle = 70, hjust = 1, vjust = 1)) +
  labs(y = "Number of Cell Lines", x = "Histology", caption = paste0(formatC(nrow(all_ccls), format = "d", big.mark = ","), " cell lines represented."))
dev.off()
```
